chronologies

### 2017-12-20 analysis/analysis_chronologies.Rmd
update chronologies

---
title: "dendro"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

@@

rwl_by_site %>% 
  write.csv(file=paste(di, "data/proto_tables/site_dendro.csv", sep=""), row.names = FALSE)

@@

rwl_by_loc %>% 
  write.csv(file=paste(di, "data/proto_tables/loc_dendro.csv", sep=""), row.names = FALSE)

@@

```{r}
# Robust mean biweith or not
cro_sjb <- chron(bai_sj, prefix = "SJ", biweight = TRUE)
cro_sjnotb <- chron(bai_sj, prefix = "SJ", biweight = FALSE)

cro_b <- cro_sjb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  select(bai_mean = SJstd, samp.depth, year, treatment)

cro_notb <- cro_sjnotb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  select(bai_mean = SJstd, samp.depth, year, treatment)

@@

aux_cro %>% ggplot(aes(x = year, y = bai_mean/100, colour=treatment)) + 
  geom_point() + geom_line() + 
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) + 
  theme_bw() + theme(panel.grid.major = element_blank()) +
  ggtitle('SJ chronology built using Biweight or Mean')
```

```{r}
# Robust mean biweith or not
cro_cab_h <- chron(bai_caH, prefix = "CA", biweight = TRUE)
cro_canotb_h <- chron(bai_caH, prefix = "CA", biweight = FALSE)

cro_cab_h_aux <- cro_cab_h %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  select(bai_mean = CAstd, samp.depth, year, treatment)

cro_canotb_h_aux <- cro_canotb_h  %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  select(bai_mean = CAstd, samp.depth, year, treatment)

@@

```{r}
# San Juan 
cro_sjH <- chrono_bai(bai_sjH)
cro_sjH$site <- 'SJ_High'

@@

cro_sj %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank()) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) 
```

@@

```{r}
# Canar 
cro_caH <- chrono_bai(bai_caH)
cro_caH$site <- 'CA_High'

@@

cro_ca %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank()) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) 
```

```{r}
# Combine and plot 
cro_sites <- rbind(cro_ca, cro_sj)

cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_line() + geom_point() + 
  theme(panel.grid = element_blank()) + facet_wrap(~loc, nrow = 2) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) 
#  geom_smooth(method= 'loess', span = 0.75, se=FALSE)
```

@@

@@

correla <- rbind(correla_ca, correla_sj)

correla %>% 
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2)  +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) + 
  facet_wrap(~metodo_correla, ncol=2) +
  theme(strip.background = element_blank())

@@

@@

---> here

>>>>

---
title: "chronologies"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

@@

rwl_by_site %>% 
  write.csv(file=paste(di, "data/dendro_summary/site_dendro.csv", sep=""), row.names = FALSE)

@@

rwl_by_loc %>% 
  write.csv(file=paste(di, "data/dendro_summary/loc_dendro.csv", sep=""), row.names = FALSE)

@@

```{r chro_sj_compare_method}
# Robust mean biweith or not
cro_sjb <- chron(bai_sj, prefix = "SJ", biweight = TRUE)
cro_sjnotb <- chron(bai_sj, prefix = "SJ", biweight = FALSE)

cro_b <- cro_sjb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  dplyr::select(bai_mean = SJstd, samp.depth, year, treatment)

cro_notb <- cro_sjnotb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  dplyr::select(bai_mean = SJstd, samp.depth, year, treatment)

@@

aux_cro %>% ggplot(aes(x = year, y = bai_mean / 100, colour=treatment)) + 
  geom_point() + geom_line() + 
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) + 
  theme_bw() + theme(panel.grid.major = element_blank()) +
  ggtitle('SJ chronology built using Biweight or Mean')
```

```{r chro_ca_compare_method}
# Robust mean biweith or not
cro_cab_h <- chron(bai_caH, prefix = "CA", biweight = TRUE)
cro_canotb_h <- chron(bai_caH, prefix = "CA", biweight = FALSE)

cro_cab_h_aux <- cro_cab_h %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  dplyr::select(bai_mean = CAstd, samp.depth, year, treatment)

cro_canotb_h_aux <- cro_canotb_h  %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  dplyr::select(bai_mean = CAstd, samp.depth, year, treatment)

@@

```{r chrono_sj_two_sites}
# San Juan 
cro_sjH <- chrono_bai(bai_sjH)
cro_sjH$site <- 'SJ_High'

@@

plot_cro_sj <- cro_sj %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                    ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + geom_point(size=1) + 
  # scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank()) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1920, 2020, by=10))

plot_cro_sj
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sj_HL.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sj, width=12, height = 4) 
```

@@

```{r chrono_ca_two_sites}
# Canar 
cro_caH <- chrono_bai(bai_caH)
cro_caH$site <- 'CA_High'

@@

plot_cro_ca <- cro_ca %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=1) + 
  # scale_colour_manual(values = c("red", "blue")) + 
  theme(panel.grid = element_blank()) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep='')))+
  scale_x_continuous(breaks = seq(1815, 2020, by=10))

plot_cro_ca
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_ca_HL.pdf') 
ggsave(filename=fileplot, plot=plot_cro_ca, width=12, height = 4) 
```

```{r chronos_4_sites}
# Combine and plot 
cro_sites <- rbind(cro_ca, cro_sj)

plot_cro_sites <- cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=1) +
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + facet_wrap(~loc, nrow = 2) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  scale_fill_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10)) 
#  geom_smooth(method= 'loess', span = 0.75, se=FALSE)

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sites.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sites, width=12, height = 8)
```

```{r chronos_4_sites_collapsed}
plot_cro_sites_collapsed <- cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  # geom_point(size=1) +
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  scale_fill_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10)) 
#  geom_smooth(method= 'loess', span = 0.75, se=FALSE)
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sites_collapsed.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sites_collapsed, width=12, height = 4)
plot_cro_sites_collapsed
```

```{r chronos_4_sites_collapsed50}
plot_cro_sites_collapsed50  <- cro_sites %>% 
  filter(year > 1949) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  # geom_point(size=1) +
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  scale_fill_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1950, 2020, by=5)) 
#  geom_smooth(method= 'loess', span = 0.75, se=FALSE)

plot_cro_sites_collapsed50
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sites_collapsed50.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sites_collapsed50, width=12, height = 4) 
plot_cro_sites_collapsed50
```

```{r chronos_4_sites_collapsed90}
plot_cro_sites_collapsed90  <- cro_sites %>% 
  filter(year > 1989) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  # geom_point(size=1) +
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  scale_fill_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1990, 2016, by=2))

plot_cro_sites_collapsed90
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sites_collapsed90.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sites_collapsed90, width=12, height = 4) 
plot_cro_sites_collapsed90
```

@@

```{r, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
# set seed
set.seed(333)

# Metodo correlation
tc <- c('spearman', 'pearson')

@@

correla <- rbind(correla_ca, correla_sj)
```

```{r correla_chronos_sites, warning=FALSE, message=FALSE, fig.width=12, fig.height=8}
correla %>% 
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2)  +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) + 
  facet_wrap(~metodo_correla, ncol=2) +
  theme(strip.background = element_blank())
```

```{r correla_chronos_sites_pearson}
correla_sites_pearson <- correla %>% filter(metodo_correla == 'pearson') %>%
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2) +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) + 
  theme(legend.position = c(.8,.7))
correla_sites_pearson
```

```{r}
fileplot <- paste0(di, '/out/chronos/correla_boot_sitesHL.pdf') 
ggsave(filename=fileplot, plot=correla_sites_pearson, width=5, height = 5) 
```

@@

set.seed(333)

@@

```{r correla_sitesSJCALH}
correla_sitesSJCALH  <- correla %>% 
  filter(metodo_correla == 'pearson') %>%
  ggplot(aes(x=size, y=estimate, colour=name_comparison)) + 
  geom_line()+ theme_bw() + ylab('Correlation coefficient') +
  xlab('Smoothing (centred moving average window size)') + 
  # geom_smooth(method = 'loess', se=FALSE) + 
  theme(panel.grid = element_blank()) +
  geom_hline(yintercept = 0, colour='gray', linetype=2) + 
  geom_line(aes(x=size, y=ci_lower, colour=name_comparison), linetype = 2) +
  geom_line(aes(x=size, y=ci_upper, colour=name_comparison), linetype = 2) +
  theme(legend.position = c(.8,.9), legend.title = element_blank())

correla_sitesSJCALH
```

```{r}
fileplot <- paste0(di, '/out/chronos/correla_boot_sitesSJCALH.pdf') 
ggsave(filename=fileplot, plot=correla_sitesSJCALH, width=5, height = 5) 
```

# Chronologies by site (SJ, CAL, CAH)

```{r}
# Compute la crono de SJ de nuevo y llamar al site SJ
cro_sjf <- chrono_bai(bai_sj)
cro_sjf$site <- 'SJ'
```

```{r crono_compara_sitesSJCALH}
# Combine and plot 
cro_sites <- rbind(cro_caL, cro_caH, cro_sjf)

## Export data of bai (chro)
write.csv(cro_sites, file=paste(di, "data/cronos_medias/cronos_sites.csv", sep=""), row.names = FALSE)

plot_cro_sitesSJCALH <- cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  scale_fill_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10))

plot_cro_sitesSJCALH
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sitesSJCALH.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sitesSJCALH, width=12, height = 5)
plot_cro_sitesSJCALH
```

```{r crono_compara_sitesSJCALH50}
plot_cro_sitesSJCALH50 <- cro_sites %>% 
  filter(year > 1949) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  scale_fill_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10)) 
plot_cro_sitesSJCALH50
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sitesSJCALH50.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sitesSJCALH50, width=12, height = 5)
```

```{r crono_compara_sitesSJCALH90}
plot_cro_sitesSJCALH90 <- cro_sites %>% 
  filter(year > 1989) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  scale_fill_manual(values = c('#7570b3','#e7298a','#1b9e77')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10))
plot_cro_sitesSJCALH90
```

```{r}
fileplot <- paste0(di, '/out/chronos/crono_compara_sitesSJCALH90.pdf') 
ggsave(filename=fileplot, plot=plot_cro_sitesSJCALH90, width=12, height = 5)
```
